Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2017-11-16 papers/cvpr2018/0_introduction.tex
final edit pass
paper: BM updates

\begin{figure}[t]
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
	}
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
	}
	\caption{Example improvement of neural reconstruction. (a) We extract 3D skeletons from pixel-based segmentation algorithms to create a 3D graph representation. Edges with high segmentation error probabilities are indicated by the red arrows. (b) We improve the accuracy of segmentation  using a graph partitioning algorithm, leveraging both local and global information.}
	\label{fig:teaser}
\end{figure}

@@

This work makes the following contributions: (1) a novel top-down method using  graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors using the 3D graph as global constraint; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over a state-of-the-art pixel-based reconstruction approach on average by \FIX{X} percent without drastically increasing the running time.

>>>>

\begin{figure}[t]
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
	}
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
	}
	\caption{Example improvement of neural reconstruction. (a) We extract 3D skeletons from pixel-based segmentation algorithms to create a 3D graph representation. Edges with high segmentation error probabilities are indicated by the red arrows. (b) We improve the segmentation accuracy using a graph partitioning algorithm, leveraging both local and global information.}
	\label{fig:teaser}
\end{figure}

@@

This work makes the following contributions: (1) a novel top-down method using  graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors using the 3D graph as global constraint; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over a state-of-the-art pixel-based reconstruction approach on average by 19.3\% without drastically increasing the running time.

### 2017-11-16 papers/cvpr2018/1_related_work.tex
paper: BM updates

\paragraph{Error-correction methods.}
Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{mojo2,haehn2014design,haehn2017guided} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
However, to our knowledge, our method is the first to extract a 3D graph from pixel-based segmentations for a true top-down error correction approach. This allows us to enforce domain-specific biology constraints and efficient graph partitioning algorithms. Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted 3D graph into the final neural reconstruction.

>>>>

\paragraph{Error-correction methods.}
Some recent research builds on top of these region-based methods to correct errors in the segmentation either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or fully automatically~\cite{rolnick2017morphological,error_correction_using_CNN}.
However, to our knowledge, our method is the first to extract a 3D graph from pixel-based segmentations for a true top-down error correction approach. This allows us to enforce domain-specific biology constraints and use efficient graph partitioning algorithms. Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. We use the method of Keuper et al.~\cite{keuper2015efficient} to partition the extracted 3D graph into the final neural reconstruction.

### 2017-11-16 papers/cvpr2018/4_results.tex
paper: BM updates

Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \FIX{X\%} and only increasing the VI merge score by \FIX{X\%}.
Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
We see significant improvements on the Kasthuri datasets (VI split reduction of \FIX{X\%} and \FIX{X\%} on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \FIX{X\%} and \FIX{X\%}). This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.

>>>>

Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by 19.3\% on the three testing datasets. 
Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
We see significant improvements on the Kasthuri datasets (VI split reduction of 27.7\% and 24.8\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of 15.2\% and 18.0\%). This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.
